\newpage
\vspace{6cm}
\section{INTRODUCTION}
\subsection{What is the Facebook client?}
\hspace{0.7cm}To begin with, Facebook is a social networking website where users can post comments, share pictures, post links to news or other interesting content, chat live, and watch short-form videos.... It was established in 2004 by Mark Zuckerberg and Edward Saverin as a school-based social network at Harvard University. Until now, it has become one of the most popular social media in the world and gained billions of users thanks to its convenience and simplicity.

\vspace{0.7cm}Facebook client is a stand-alone application running on clients’ machines.	It utilizes the core technologies of the Facebook platform to integrate Facebook’s News Feed, Notifications and other feature for the users.

\vspace{0.7cm}In this project, our group tried to make a fundamental and primitive Facebook client. 

\subsection{Why do people need our application?}
\hspace{0.7cm}In our opinion, we think that the Facebook client our group created could benefit users in many ways. Firstly, the most obvious reason is that this application bases on the Facebook platform, so basically, it can be considered as a tool to connect to the social network where people can perform tasks such as reading friends’ status, watching short videos, commenting... Moreover, our program provides a convenient and easy way of interaction with Facebook. Due to the fact that this is a mobile application, people can access to the social network anywhere just by their phones.